The low-frequency Murchison radio environment:\\interference analysis and mitigation

### 2014-09-05 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Work on article

\begin{table}
\caption{..}\label{tbl:obs-list}
\begin{tabular}{|l|l|r|r|}
\hline
\textbf{Project} &\textbf{Date} & \textbf{Frequencies (MHz)} & \textbf{Duration} \\
\hline
EoR   & 2013-08-23 & 138.9--197.7 & 3h\\
GLEAM & 2013-08-25 & 72.3--133.8, 138.8--230.8 & 7h \\
EoR   & 2013-08-26 & 138.9--197.7 & 6h \\
GLEAM & 2013-11-25 & 72.3--133.8, 138.8--230.8 & 7h \\
GLEAM & 2014-03-16 & 72.3--133.8, 138.8--230.8 & 7h \\
EoR   & 2014-04-10 & 138.9--197.7 & 6h \\
GLEAM & 2013-11-05 & 72.3--133.8, 138.8--230.8 & 7h \\
EoR   & 2014-02-05 & 138.9--197.7 & 6h\\
GLEAM & 2014-03-17 & 72.3--133.8, 138.8--230.8 & 7h\\
GLEAM & 2014-06-18 & 72.3--133.8, 138.8--230.8 & 7h \\
RFI test&2014-08-27& 131.2--161.9 & 2$\times$8 m \\
\hline
\multicolumn{3}{|r|}{\textbf{Total}} & \textbf{63h} \\
\hline
\end{tabular}
\end{table}

@@

The MWA EoR project observes primarily in the 138.9--197.7~MHz range, covering the HI 21-cm line with redshift 6.1--9.2. Because the MWA has a 30.72~MHz instantaneous bandwidth, this range has been split up so that each night observes with a central frequency of either 154.2 or 182.4~MHz, with an overlap of 2.6 MHz. In these observations, the beamformers track a selected EoR field such that the sensitivity of the primary beam is maximal towards the field.

@@

\begin{itemize}
 \item List obs dates
\end{itemize}

@@

\noindent\begin{figure*}
% obs data: 1061583576, 2013-08-26.
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/150_2_mhz_example}\includegraphics[width=9.1cm]{img/150_2_mhz_flagged}
\caption{Short RFI burst of 2 s centred on 150.17 MHz}
\label{fig:150_2}
\end{center}
\end{figure*}

\noindent\begin{figure*}
% obs data: 1061583576, 2013-08-26.
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/156_7_mhz_example}\includegraphics[width=9.1cm]{img/156_7_mhz_flagged}
\caption{A weakly-observed transmitter centred on 156.66 MHz.}
\label{fig:156_7}
\end{center}
\end{figure*}

@@

\begin{itemize}
 \item An example of RFI found (e.g., the EoR DVB, 
 \item Percentages per 
 \item Performance
\end{itemize}

>>>>

\begin{table*}
\caption{List of observations used in the analyses}\label{tbl:obs-list}
\begin{tabular}{|l|l|r|r|r|c|}
\hline
\textbf{Project} &\textbf{Date} & \textbf{Frequencies (MHz)} & \textbf{Duration} & RFI & DVB? \\
\hline
EoR   & 2013-08-23 & 138.8--197.7              & 3h & 0.53\% & ---\\
GLEAM & 2013-08-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.94\% & no \\
EoR   & 2013-08-26 & 138.8--197.7              & 6h & 0.81\% & ---\\
GLEAM & 2013-11-05 & 72.3--133.8, 138.8--230.8 & 7h &  1.3\% & no \\
GLEAM & 2013-11-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.69\% & no \\
EoR   & 2014-02-05 & 138.8--197.7              & 6h & 0.54\% & -- \\
GLEAM & 2014-03-16 & 72.3--133.8, 138.8--230.8 & 7h & 0.79\% & no \\
GLEAM & 2014-03-17 & 72.3--133.8, 138.8--230.8 & 7h & 1.64\% & yes \\
EoR   & 2014-04-10 & 138.8--197.7              & 6h & 0.68\% & ---\\
GLEAM & 2014-06-18 & 72.3--133.8, 138.8--230.8 & 7h & 0.98\% & no \\
RFI test&2014-08-27& 131.2--161.9     & 2$\times$8 m& 1.85\% & --- \\
\hline
\multicolumn{3}{|r|}{\textbf{Total}} & \textbf{63h} & \textbf{0.97\%} & \textbf{1/6}\\
\hline
\end{tabular}
\end{table*}

@@

The MWA EoR project observes primarily in the 138.9--197.7~MHz range, covering the HI 21-cm line with redshift 6.1--9.2. Because the MWA has a 30.72~MHz instantaneous bandwidth, this range has been split up so that each night observes with a central frequency of either 154.2 or 182.4~MHz, with an overlap of 2.6 MHz. In these observations, the selected EoR field is tracked byt the primary beam, such that the sensitivity towards the field is maximal.

@@

@@

\noindent\begin{figure*}
% obs data: 1061583576, 2013-08-26.
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/150_2_mhz_example}\includegraphics[width=9.1cm]{img/150_2_mhz_flagged}
\caption{Short RFI burst of 2 s centred on 150.17 MHz. This shows that flagging at high time and frequency resolution is necessary to accurately detect RFI.}
\label{fig:150_2}
\end{center}
\end{figure*}

\noindent\begin{figure*}
% obs data: 1061583576, 2013-08-26.
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/156_7_mhz_example}\includegraphics[width=9.1cm]{img/156_7_mhz_flagged}
\caption{A weakly-observed transmitter centred on 156.66 MHz. Although it is hard to identify in such a time-frequency plot, the same frequency is flagged in several correlations, and it can therefore be assumed this is real RFI. This is an example in which the AOFlagger detect an event that would not be detected by regular thresholding. }
\label{fig:156_7}
\end{center}
\end{figure*}

\noindent\begin{figure}
% obs data: 1061583576, 2013-08-26.
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/dvb_example}
\caption{RFI from Digital Video Broadcasting (DVB). Because of its broadband nature, this kind of RFI is not well flagged in the initial AOFlagger step. It is detected by a later step by checking the global statistics. This type of RFI makes most of the 30.72~MHz bandwidth unusable. It is not seen very often (1 out of 6 observed nights). }
\label{fig:dvb_example}
\end{center}
\end{figure}

@@

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/2014-03-17-dvb-stddevs}\vspace{-1cm}
\caption{..}
\label{fig:rfi-per-set}
\end{center}
\end{figure*}

\begin{itemize}
 \item Total RFI statistics
 \item Percentages + stddev per frequency + discuss
 \item An example of RFI found (e.g., the EoR DVB, ..)
 \item Performance
 \item Log N log S Histograms
\end{itemize}
